The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-08-05 src/science/paper.tex
Go back to longer version.

    \floatfoot{\noindent \textit{Note:}
        A~description of the model can be found in Supplementary
        Material~\ref{sec:model}. Figure~\ref{fig:model_contacts_infections} shows the
        influence of an agent's contacts to other agents on infections. Demographic
        characteristics set the baseline number of contacts in different networks
        ($\eta$). The agents may reduce the number of contacts due to NPIs, showing
        symptoms, or testing positively for SARS-CoV-2 ($\tau$). Infections may occur
        when a susceptible agent meets an infectious agent; the probability depends on
        the type of contact ($\beta_c$), on seasonality ($\kappa_{c}$), and on NPIs
        ($\rho_{c,\:t}$). If infected, the infection progresses as depicted in
        Figure~\ref{fig:model_disease_progression}. If rapid tests are available,
        agents' demand is modeled as in Figure~\ref{fig:model_rapid_tests}. All reasons
        trigger a test only for a fraction of individuals depending on an individual
        compliance parameter; the thresholds for triggering test demand differ across
        reasons and they may depend on calendar time ($\pi_{c,\:t}$ and $\tau_{c,\:t}$).
        Figure~\ref{fig:model_official_cases} shows the model of translating all
        infections in the simulated data to age-specific recorded infections. The model
        uses data on the aggregate share of recorded cases ($\psi$), the share of
        positive PCR tests triggered by symptoms ($\chi_{symptom}$), and the false
        positive rate of rapid tests ($p_{positive|infected,\;i,\:t}$). The lower part
        of the graph is relevant only for periods where rapid tests are available. All
        parameters are explained in Appendix~\ref{sub:param_tables}.}
\end{figure}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and calibrate the model's many
parameters.\footnote{See Supplementary Material~\ref{sec:data_and_parameters} for a
    complete description.} Contact diaries yield pre-pandemic distributions of contacts for
different contact types and their assortativity by age group. Mobility data is used to
model the evolution of work contacts. School and daycare policies can be incorporated
directly from official directives. Administrative records on the number of tests,
vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of some NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data (see \cite{McFadden1989} for the general method). In our
application, we keep the number of free parameters low in order to avoid overfitting.
The data features to be matched include official case numbers for each age group and
region, deaths, and the share of the B.1.1.7 strain.

@@

    \floatfoot{\noindent \textit{Note:} Data sources are described in Supplementary
        Material~\ref{sec:data_and_parameters}. Age- and region-specific analogues to
        Figure~\ref{fig:aggregated_fit} can be found in Supplementary Material
        \ref{subsec:fit_results}. For legibility reasons, all lines in
        Figure~\ref{fig:stringency_infectious_contacts} are rolling 7-day averages. The
        Oxford Response Stringency Index is scaled as $2 \cdot (1 -  x / 100)$, so that
        a value of one refers to the situation at the start of our sample period and
        zero means that all NPIs included in the index are turned on. The other lines in
        Figure~\ref{fig:stringency_infectious_contacts} show the product of the effect
        of contact reductions, increased hygiene regulations, and seasonality. See
        Appendix~\ref{subsec:policies} for separate plots of the three factors by
        contact type.}
\end{figure}

>>>>

    \floatfoot{\noindent \textit{Note:}
        A~description of the model can be found in Supplementary
        Material~\ref{sec:supplementary_text}. Figure~\ref{fig:model_contacts_infections}
        shows the influence of an agent's contacts to other agents on infections.
        Demographic characteristics set the baseline number of contacts in different
        networks ($\eta$). The agents may reduce the number of contacts due to NPIs,
        showing symptoms, or testing positively for SARS-CoV-2 ($\tau$). Infections may
        occur when a susceptible agent meets an infectious agent; the probability depends
        on the type of contact ($\beta_c$), on seasonality ($\kappa_{c}$), and on NPIs
        ($\rho_{c,\:t}$). If infected, the infection progresses as depicted in
        Figure~\ref{fig:model_disease_progression}. If rapid tests are available, agents'
        demand is modeled as in Figure~\ref{fig:model_rapid_tests}. All reasons trigger a
        test only for a fraction of individuals depending on an individual compliance
        parameter; the thresholds for triggering test demand differ across reasons and
        they may depend on calendar time ($\pi_{c,\:t}$ and $\tau_{c,\:t}$).
        Figure~\ref{fig:model_official_cases} shows the model of translating all
        infections in the simulated data to age-specific recorded infections. The model
        uses data on the aggregate share of recorded cases ($\psi$), the share of
        positive PCR tests triggered by symptoms ($\chi_{symptom}$), and the false
        positive rate of rapid tests ($p_{positive|infected,\;i,\:t}$). The lower part of
        the graph is relevant only for periods where rapid tests are available. All
        parameters are explained in Appendix~\ref{sub:param_tables}.}
\end{figure}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and calibrate the model's many
parameters.\footnote{See Supplementary Material~\ref{sec:materials_and_methods} for a
    complete description.} Contact diaries yield pre-pandemic distributions of contacts for
different contact types and their assortativity by age group. Mobility data is used to
model the evolution of work contacts. School and daycare policies can be incorporated
directly from official directives. Administrative records on the number of tests,
vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of some NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data (see \cite{McFadden1989} for the general method). In our
application, we keep the number of free parameters low in order to avoid overfitting.
The data features to be matched include official case numbers for each age group and
region, deaths, and the share of the B.1.1.7 strain.

@@

    \floatfoot{\noindent \textit{Note:} Data sources are described in Supplementary
        Material~\ref{sec:materials_and_methods}. Age- and region-specific analogues to
        Figure~\ref{fig:aggregated_fit} can be found in Supplementary Material
        \ref{subsec:fit_results}. For legibility reasons, all lines in
        Figure~\ref{fig:stringency_infectious_contacts} are rolling 7-day averages. The
        Oxford Response Stringency Index is scaled as $2 \cdot (1 -  x / 100)$, so that
        a value of one refers to the situation at the start of our sample period and
        zero means that all NPIs included in the index are turned on. The other lines in
        Figure~\ref{fig:stringency_infectious_contacts} show the product of the effect
        of contact reductions, increased hygiene regulations, and seasonality. See
        Appendix~\ref{subsec:policies} for separate plots of the three factors by
        contact type.}
\end{figure}
